---
title: "Netflix_analysis"
By: "Siddhesh Sreedar"
output: github_document
---

```{r}
library(rmarkdown)
```

```{r setup, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(error = TRUE)
```

```{r global_options}
knitr::opts_chunk$set(fig.path='Figs/')
```

```{r}
library(knitr)
opts_chunk$set(dev="png")
```

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
```


```{r}
netflix<- read.csv("~/Desktop/NetflixViewingHistory.csv")
dim(netflix)
```

Selecting only the titles and not the episodes.

```{r message=FALSE, warning=FALSE}
netflix<-netflix%>%separate(Title,c("Title","col1","col2"),sep=":")
netflix$col1<-NULL
netflix$col2<-NULL
binge<-netflix%>%select(Title,Date)%>%group_by(Title,Date)%>%summarise(total=n())%>%arrange(desc(total))
binge<-as.data.frame(binge)
```


Shows binged:
```{r}
head(binge)
```


According to sources a binge is when you watch 2-6 episodes in one sitting,
so for this analysis I will take 6 episodes.

```{r message=FALSE, warning=FALSE}
binge<-subset(binge,total>=6)
library(ggplot2)
binge<-binge%>%top_n(10)
ggplot(binge,aes(total,Title))+geom_bar(stat = "identity")
```

So the most binged show was "big mouth" dated on 6/10/2018.


```{r message=FALSE, warning=FALSE}
view<-netflix%>%select(Title,Date)%>%group_by(Title)%>%summarise(total=n())%>%arrange(desc(total))
view<-as.data.frame(view)
view<-view%>%top_n(10)
ggplot(view,aes(total,Title))+geom_bar(stat = "identity")
```

most viewed show is "Friends".^


time analysis of netflix data:
```{r message=FALSE, warning=FALSE}
library(lubridate)

netflix$Date<-dmy(netflix$Date)
netflix$day<-weekdays(netflix$Date)
day_analysis<-netflix%>%count(Date)%>%arrange(desc(n))
head(day_analysis)
```

2019-03-09 14 and 2020-02-15 14 :the two days where i binged the most shows and movies.

```{r}
ggplot(day_analysis,aes(Date,n))+geom_bar(stat = "identity")
```

we see that the amount of netflix shows/movies consumed has increased over the years.^


daily consumption through all the years:
```{r}
day_analysis$year<-year(day_analysis$Date)
day_analysis$month<-month(day_analysis$Date)
day_analysis$day<-weekdays(day_analysis$Date)
day_analysis$week<-ceiling(day(day_analysis$Date)/7)
a<-day_analysis$month
day_analysis$month<-ifelse(a==1,"jan",ifelse(a==2,"feb",ifelse(a==3,"mar",ifelse(a==4,"apr",ifelse(a==5,"may",ifelse(a==6,"jun",ifelse(a==7,"jul",ifelse(a==8,"aug",ifelse(a==9,"sep",ifelse(a==10,"oct",ifelse(a==11,"nov","dec")))))))))))

ggplot(day_analysis,aes(week,day))+geom_tile(aes(fill=n))+facet_grid(year~month)+scale_fill_gradient(low = "#FFD000", high = "#FF1919")
```


which day of the week is my consumption the highest:
```{r}
ggplot(day_analysis,aes(day,n))+coord_polar()+ geom_col(fill = "#5b59d6")
```

thursdays is the most^


which month of the year is my consumption the highest
```{r}
ggplot(day_analysis,aes(month,n))+coord_polar()+ geom_col(fill = "#5b59d6")
```

june is the highest^



which month of all the years is my consumption the highest
```{r}
day_analysis$month_year<-paste(day_analysis$month,day_analysis$year,sep = " ")
ggplot(day_analysis,aes(month_year,n))+coord_polar()+ geom_col(fill = "#5b59d6")
```

march 2020 is the highest^



2020 comparision with other years(from 2017)
consisdering only the first 6 months:

```{r}
day_analysis<-subset(day_analysis,year!=2016)
day_analysis$m<-month(day_analysis$Date)
day_analysis<-subset(day_analysis,m<=6)

ggplot(day_analysis,aes(n,month))+geom_bar(stat = "identity")+facet_grid(~year)
```


we see that their is very high consumption in the year 2020 compared to the other years.
one of the reasons could be the spread of the COVID-19 virus which has forced people to stay at home and with a lot of time in our hands , the consumption of netflix has dramatically increased.






